### 2014-09-29 PrivacyProtection-2014-09-09.tex

\subsubsection{Conflict of Interests (Figure \ref{figure:Live+Gov Conflicts of Interests})}

%\includegraphics{../diagrams/png/conflict-of-interests.png}
\input{./figures/LG-Conflicts-Of-Interests}

>>>>

\subsubsection{Conflicts of Interests}
\label{subsubsection:Conflicts of Interests}
This section outlines the Conflicts of Interests (Figure \ref{figure:Live+Gov Conflicts of Interests}) between the actors of the proposed IT system architecture. 
The individual interests of all actors is already described in the previous section and are not elaborated any further.
The emphasis here is put on the existing conflicts.

\input{./figures/LG-Conflicts-Of-Interests}
